A standardized framework for risk-based assessment of treatment effect heterogeneity in observational healthcare databases

### 2021-04-28 submission/manuscript.rmd
add missing reference

More recently, “predictive” HTE analyses have been described (and contrasted
with “one-variable-at-a-time” subgroup analysis) as approaches that provide
predictions of potential outcomes in a particular patient with one intervention
versus an alternative, taking into account multiple relevant patient
characteristics. One promising approach is “risk modeling”, in which treatment
effects are estimated in strata of predicted risk [@Kent2010; @Kent2018]. Such
a risk-based approach first stratifies patients according to baseline risk
predictions, using either an existing or an internally developed risk prediction
model [@Kent2010]. Then, relative and absolute treatment effects are estimated
within risk strata.

>>>>

More recently, “predictive” HTE analyses have been described (and contrasted
with “one-variable-at-a-time” subgroup analysis) as approaches that provide
predictions of potential outcomes in a particular patient with one intervention
versus an alternative, taking into account multiple relevant patient
characteristics [@Varadhan2013]. One promising approach is “risk modeling”, in
which treatment effects are estimated in strata of predicted risk [@Kent2010;
@Kent2018]. Such a risk-based approach first stratifies patients according to
baseline risk predictions, using either an existing or an internally developed
risk prediction model [@Kent2010]. Then, relative and absolute treatment
effects are estimated within risk strata.
